A graph-based approach for interactive evolutionary computation

### 2017-01-17 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Starting Intro

\section{Introduction}
% no \IEEEPARstart
This demo file is intended to serve as a ``starter file''
for IEEE conference papers produced under \LaTeX\ using
IEEEtran.cls version 1.8b and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

\hfill mds

\hfill August 26, 2015

\subsection{Subsection Heading Here}
Subsection text here.
\cite{Sims:1991}

>>>>

\section{Introduction}
Interactive Evolutionary Algorithms (IEAs): are standard EAs whose
fitness evaluations are performed by persons with in an interactive 
system.  Thus, the main loop of the EA need a human intervention for
the quality assessment of each proposed solution. These systems have an
inherent drawback araising from the very nature of the model, namely,
the human fatigue caused by the interaction. Some authors have already
tried to address this basic problem \cite{Frade:2010:EvoGAMES}.
nevertheless, IEAs have demonstrated their ability for effectively
producing art and design \cite{Bentley:1999:intro,Sims:1991,todd:1992},.
as well as other domains \cite{ie1}.

,
\subsection{Subsection Heading Here}
Subsection text here.
\cite{Sims:1991}
